Making Sequential Programs Deterministic

### 2019-03-28 experiments.tex
nondex bullets

\section{Evaluation}
\subsection{NONDEX case study}
\begin{table}[]
    \begin{tabular}{|l|l|l|l|l|l|}
        \hline
        Benchmark & Recall? & Error message source & # annotations & Type of annotation added & Comments \\ \hline
        P1 &  &  &  &  &  \\
        P2 &  &  &  &  &  \\
        P3 &  &  &  &  &  \\ 
        P4 &  &  &  &  &  \\ 
        P5 &  &  &  &  &  \\ 
        P5 &  &  &  &  &  \\ 
        P6 &  &  &  &  &  \\ 
        P6 &  &  &  &  &  \\
        P7 &  &  &  &  &  \\ 
        P7 &  &  &  &  &  \\
        P7 &  &  &  &  &  \\
        P7 &  &  &  &  &  \\
        P7 &  &  &  &  &  \\
        P8 &  &  &  &  &  \\
        P8 &  &  &  &  &  \\
        P8 &  &  &  &  &  \\
        P9 &  &  &  &  &  \\
        P10 &  &  &  &  &  \\
        P10 &  &  &  &  &  \\
        P11 &  &  &  &  &  \\
        P12 &  &  &  &  &  \\
        P13 &  &  &  &  &  \\
        P14 &  &  &  &  &  \\
        P15 &  &  &  &  &  \\
        P15 &  &  &  &  &  \\
        P16 &  &  &  &  &  \\
        P17 &  &  &  &  &  \\
        P18 &  &  &  &  &  \\
        P19 &  &  &  &  &  \\
        P19 &  &  &  &  &  \\
        P19 &  &  &  &  &  \\
        P20 &  &  &  &  &  \\
        P20 &  &  &  &  &  \\
        P21 &  &  &  &  &  \\
        P21 &  &  &  &  &  \\ \hline
    \end{tabular}
\end{table}

>>>>

\section{Evaluation}
\subsection{NONDEX case study}
Methodology:
\begin{itemize}
    \item Objective: Measure recall.
    \item Benchmarks from NONDEX paper.
    \item That paper gives flaky test class and source of flakiness (nondeterministic method call).
    \item Look at the source method under test.
    \item annotate the local arrays and collections (This has been mostly sufficient for recall)
\end{itemize}

Discussion of results:

\begin{itemize}
    \item Refer to table and describe it.
    \item P7: same source causing multiple tests to be flaky
    \item Example for class.GetDeclaredMethod() and show annotations
    \item Example for HashMap.entrySet() and show annotations.
    \item qualitative comparison: orthogonal techniques (reporting tests vs reporting source locations).
    \item From NonDex paper: "manually inspecting these failures was rather challenging"
\end{itemize}

\begin{table}[]
    \begin{tabular}{|p{1.5cm}|p{1cm}|p{3cm}|p{4cm}|p{2cm}|p{1.5cm}|}
        \hline
        Benchmark & Recall? & Error message source & Error msg & \#annotations & Annotation type  \\ \hline
        P1 & Yes & FieldAccess.java: [102,87] & assignment type incompatible &  &   \\
        P2 & MI &  &  &  &  \\
        P3 & Yes & DateTimeZone.java: [731,27] &  return type incompatible&  &  \\ 
        P4 & MI &  &  &  &  \\ 
        P5 & src &  &  &  &  \\ 
        P5 & src &  &  &  &  \\ 
        P6 & MI &  &  &  &  \\ 
        P6 & MI &  &  &  &  \\
        P7(test error) & Yes & checker/ tests/ determinism/P71.java: 5 & return type incompatible &  &  \\ 
        P7(2) & Yes & FieldUtils.java: [219,84] & assignment type incompatible &  &  \\
        P7(2) & Yes & Reflection ToStringBuilder.java: [543,65]  & assignment type incompatible &  &  \\
        P7(2) & Yes & HashCodeBuilder.java: [193,69]  & assignment type incompatible &  &  \\
        P7(2) & Yes & CompareToBuilder.java: [322,65] & assignment type incompatible &  &  \\
        P7(2) & Yes & EqualsBuilder.java: [419,69]  & assignment type incompatible &  &  \\
        P7 & Yes & FieldUtils.java: [200,69] & assignment type incompatible & &  \\
        P7 & Yes & FieldUtils.java: [219,84] & assignment type incompatible &  &  \\
        P7 & Yes & FieldUtils.java: [240,86] & assignment type incompatible &  &  \\
        P8 & RM &  &  &  &  \\
        P8 & RM &  &  &  &  \\
        P8 & RM &  &  &  &  \\
        P9 & MI &  &  &  &  \\
        P10 & crash &  &  &  &  \\
        P10 & crash &  &  &  &  \\
        P11 & MI &  &  &  &  \\
        P12 & MI &  &  &  &  \\
        P13 & crash &  &  &  &  \\
        P14 & MI &  &  &  &  \\
        P15 & MI &  &  &  &  \\
        P15 & MI &  &  &  &  \\
        P16 & Yes & MethodSorter.java: [56,61]  & assignment type incompatible &  &  \\
        P17 & Yes &  &  &  &  \\
        P18 & src &  &  &  &  \\
        P19 & MI &  &  &  &  \\
        P19 & MI &  &  &  &  \\
        P19 & MI &  &  &  &  \\
        P20 & MI &  &  &  &  \\
        P20 & MI &  &  &  &  \\
        P21 & MI &  &  &  &  \\
        P21 & MI &  &  &  &  \\ \hline
    \end{tabular}
\end{table}
